Trafficking synaptic materials in complex morphologies involves tradeoffs in speed and precision

### 2015-08-18 paper.tex
add title

\documentclass[fleqn,10pt]{wlpeerj}
\title{Article Title}

@@

One non-obvious prediction of this analysis is that transport to distal compartments should be quickened by allowing higher levels of $u$ into the proximal compartments at steady-state (Fig. 3E). This might be tested experimentally by characterizing the convergence time of a retrogradely transported molecule that aggregates at recently activated synapses, such as \textit{Arc} mRNA (\cite{Steward_1998}, see discussion). To illustrate this in the model CA1 cell, we characterized the time course of transport to the distal apical dendrite (stimulating stratum lacunosum/moleculare), proximal apical dendrite (stimulating stratum radiatum), entire apical dendrite (stimulating both layers), and entire cell (seizure). Interestingly, the model converged more slowly to distal input alone, than to paired distal and proximal input, or to an entirely uniform distribution (Fig. 3F).

>>>>

\documentclass[fleqn,10pt]{wlpeerj}
\title{Trafficking synaptic materials in complex morphologies involves tradeoffs in speed and precision}

@@

One non-obvious prediction of this analysis is that transport to distal compartments should be quickened by allowing higher levels of $u$ into the proximal compartments at steady-state (Fig. 3E). This might be tested experimentally by characterizing the convergence time of a retrogradely transported molecule that aggregates at recently activated synapses, such as \textit{Arc} mRNA (\citet{Steward_1998}, see discussion). To illustrate this in the model CA1 cell, we characterized the time course of transport to the distal apical dendrite (stimulating stratum lacunosum/moleculare), proximal apical dendrite (stimulating stratum radiatum), entire apical dendrite (stimulating both layers), and entire cell (seizure). Interestingly, the model converged more slowly to distal input alone, than to paired distal and proximal input, or to an entirely uniform distribution (Fig. 3F).
